Rmarkdown Features

### 2018-03-24 1062_class/eco_model/HW/W2/HW2.rmd
update

    return 0;
}
```

@@

    return 0;
}
```

>>>>

    return 0;
}
```
Download [source1.c](https://minhaskamal.github.io/DownGit/#/home?url=https://github.com/liao961120/local_depend/blob/master/1062_class/eco_model/HW/W2/source1.c){target="_blank"}

@@

    return 0;
}
```
Download [source2.c](https://minhaskamal.github.io/DownGit/#/home?url=https://github.com/liao961120/local_depend/blob/master/1062_class/eco_model/HW/W2/source2.c){target="_blank"}

### 2018-03-24 DiagrammeR/rmd_features.rmd
update

---
title: "Rmarkdown Features"
subtitle: "This is subtitle"
author: Yongfu Liao
date: March 18, 2018
bibliography: ./citation/neanderthals.bib
csl: ./citation/apa-no-doi-no-issue.csl
link-citations: yes
output:
  html_document:
    css: ../style_sheets/style.css
    df_print: kable
    code_folding: show
    toc: true
    toc_depth: 4
    toc_float: true
---
<!--more-->

@@

>>>>

---
title: "Rmarkdown Features"
subtitle: "This is subtitle"
author: Yongfu Liao
date: March 18, 2018
bibliography: ./citation/neanderthals.bib
csl: ./citation/apa-no-doi-no-issue.csl
link-citations: yes
output:
  html_document:
    css: ../style_sheets/style.css
    df_print: kable
    toc: true
    toc_depth: 4
    toc_float: true
---

@@

### Passing Matrix Object

#### Setup

Add `results='asis'` to r code chunk option.
```{r results='asis'}
library(mat2tex)
mt <- c(1,2)
"$A =" %_% xm(mt,0) %_%"_{2 \\times 1}$"
```

#### Include Matrix in Text

![](mat2tex.png){width=60% height=auto}

renders as:

<div class="success">
This is the variable `mt`,
```{r results='asis', echo=FALSE}
library(mat2tex)
mt <- matrix(1:4, 2,2)
"$A =" %_% xm(mt,0) %_%"^{-1}$"
```
, which is a matrix.
</div>

Check [here](http://markheckmann.github.io/mat2tex/){target=_blank""} for more information.
